---
title: "EDS 212 Day 5 Comp 1"
format: 
  html: 
    code-fold: true
    code-summary: "Show me the code!"
editor: visual
execute:
  echo: true
  warning: false
---

```{r}
library(tidyverse)
```

## Explore the starwars dataset

-   look at the first 6 lines of starwars

-   find the dimensions of starwars

-   make a histogram of character heights

-   make a scatterplot of height vs. weight

```{r}
head(starwars)

names(starwars)

dim(starwars)
```

```{r}
ggplot(data = starwars, aes(x = height)) + geom_histogram(fill = "blue", color = "black") + theme_minimal()
```

```{r}
ggplot(data = starwars, aes(x = height, y = mass)) + geom_point() + theme_minimal()
```

## Calculate Summary statistics

use mean() function to find means.

Use sd() function to find standard deviations.

```{r}
# without "na.rm = TRUE", returns "NA" because there are missing values in this column
mean_height <- mean(starwars$height, na.rm = TRUE)

mean_height
```

Find and store the standard deviation of character heights

```{r}
sd_height <- sd(starwars$height, na.rm = TRUE)

sd_height
```

## In-line reporting using code outputs

The mean height of star wars characters is `r mean_height` cm with a standard deviation of `r sd_height` cm.

use \`\` ! This creates more reproducible work!
